Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-18 paper/icml_drau/intro.tex

In this paper we focus on the sensitivity to time discretization of DRL
approaches, such as what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$. One
would expect that decreasing time discretization, or equivalently
shortening reaction time, should only improve agent performance.
Robustness to time discretization is especially relevant in
\emph{near-continuous} environments, which includes most continuous
control environments, robotics, and many video games.  (We focus on
near-continuous time because this leads to a clear framework, but the
approach below would be relevant in any setting in which the advantage of
any single individual action is small compared to the total return.)%, for instance, long time horizon problems.

Standard approaches based on estimation of state action
value functions, such as
\emph{Deep $Q$-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}) are not robust to changes in time discretization. This is shown experimentally in Sec.~\ref{sec:exp}. 
Intuitively, as the discretization timestep
decreases, the effect of individual actions on the total return decreases
too: $Q(s,a)$ is the value of playing action $a$ then playing optimally,
and if $a$ is only maintained for a very short time its advantage over
other actions will be accordingly small. (This continuity effect occurs even with a
well-adjusted decay factor $\gamma$.)

>>>>

In this paper we focus on the sensitivity to time discretization of DRL
approaches, such as what happens when an agent receives $50$ observations
and is expected to take $50$ actions per second instead of $10$.
In principle, decreasing time discretization, or equivalently
shortening reaction time, should only improve agent performance.
Robustness to time discretization is especially relevant in
\emph{near-continuous} environments, which includes most continuous
control environments, robotics, and many video games.  
(We focus on
near-continuous time because this leads to a clear framework, but the
approach below would be relevant in any setting in which the advantage of
any single individual action is small compared to the total return.)%, for instance, long time horizon problems.

Standard approaches based on estimation of state-action
value functions, such as
\emph{Deep $Q$-learning} (DQN~\citep{dqn} and \emph{Deep deterministic policy
gradient} (DDPG~\citep{ddpg}) are not at all robust to changes in time discretization. This is shown experimentally in Sec.~\ref{sec:exp}. 
Intuitively, as the discretization timestep
decreases, the effect of individual actions on the total return decreases
too: $Q(s,a)$ is the value of playing action $a$ then playing optimally,
and if $a$ is only maintained for a very short time its advantage over
other actions will be accordingly small. (This continuity effect occurs even with a
well-adjusted decay factor $\gamma$.)
